\section{Future Plans}
\paragraph{}
At the time of writing, I am undecided whether I want to further my education at
a post-secondary school, or whether I want to start working right away. I can
assuredly say that BOCES has properly prepared me to reach my goals. Choosing
to further my knowledge of graphic design was one of the best choices I have
made. Paired with my intimate knowledge of information technology, I have
excelled in the graphics design course. Although I only attended one year of
graphics design, my in-depth knowledge of information technology helped
tremendously in catching up and even surpassing students who have taken the
course for the full two years.
\par

\section{Interests}
\paragraph{}
Photography, videography, audio engineering, and typography are four fields of
interest that I have within my trade. 
\par

\subsection{Photography}
\paragraph{}
My interest in photography started to
develop when I would look at the work of urban explorers, who would take
pictures of the abandoned or off limits areas they had been in. The way they
could take the ordinary and make it extraordinary amazed me, another genre of
photography that caught my interest is industrial photography. Being able to see
the inner-workings of often complex infrastructure and machines gave me an
appreciation for something otherwise not thought of often. My most significant
accomplishment in photography would have to be when I volunteered to take
photographs for a cookbook that the DCMO BOCES culinary class was making. It
not only gave me practical experience with using a DSLR, but gave me the
opportunity to learn Adobe Lightroom, a professional photo enhancement program.
\par

\subsection{Videography}
\paragraph{}
My passion for videography was inspired mostly by youtubers, who would always
produce quality content that was on par or exceeded that of television.

\begin{itemize}
	\item \href{https://www.youtube.com/channel/UCE1jXbVAGJQEORz9nZqb5bQ}{Ahoy}
	\item \href{https://www.youtube.com/channel/UClfEht64_NrzHf8Y0slKEjw}{Alternate History Hub}
	\item \href{https://www.youtube.com/channel/UC2C_jShtL725hvbm1arSV9w}{CGP Grey}
	\item \href{https://www.youtube.com/user/LinusTechTips}{Linus Tech Tips}
	\item \href{https://www.youtube.com/channel/UCJkMlOu7faDgqh4PfzbpLdg}{Nerdwriter}
	\item \href{https://www.youtube.com/channel/UCYxrnDjNQZIs_aAcdhqSveg}{Rob Dyke}
	\item \href{https://www.youtube.com/user/TheUnknownCameraman}{The Unknown Camera Man}
	\item And many more
\end{itemize}

The thought that someone who didn't have the resources a TV show does making
quality content that supersedes that of TV amazes me. I've mostly experimented
with color correction via Adobe Speedgrade, a professional color grading
solution.
\par

\subsection{Audio Engineering}
\paragraph{}
My passion for audio engineering was spurred on by the subreddit \href{https://www.reddit.com/r/fieldrecording/}{r/fieldrecording},
and the ambient label \href{https://cryochamber.bandcamp.com/}{Cryo Chamber}.
The way the artists were able to make cinematic experiences from the most
ordinary of sounds interested me. The atmospheric, immersive experience created
by listening to the albums are no less then breathtaking. I have some experience
authoring \href{https://theodoretubbs.bandcamp.com/}{my own field recordings}.
\par

\subsection{Typography}
\paragraph{}
Typography is an interest that I have taken up this year. Ever since high-school
I have used a markup language called \LaTeX{} to author my documents. some of my
works can be found at:
\par

\begin{itemize}
	\item \href{https://github.com/AdrianKoshka/Papers}{AdrianKoshka/Papers}
	\item \href{https://github.com/AdrianKoshka/viscom-projects}{AdrianKoshka/viscom-projects}
	\item \href{https://github.com/AdrianKoshka/nths-papers}{AdrianKoshka/nths-papers}
	\item \href{https://github.com/AdrianKoshka}{And more can be found on my github account}
\end{itemize}

\section{Volunteering / Community Service}

\subsection{Cybertech}
\paragraph{}
I have been volunteering at the computer repair shop in Norwich, NY since
December of 2014. I've done such things as:

\begin{itemize}
	\item {Fixed various issues with software and hardware.}
	\item {Conversed with clients to help diagnose issue.}
	\item {Explained things to clients in a way they could understand.}
	\item {Have gone on house and business calls.}
	\item {Endorsed the use of Open Source software.}
	\item {Introduced Linux as a daily driver, and great debugging tool.}
	\item {Helped setup network infrastructure to improve the repair work-flow.}
\end{itemize}
\par

\paragraph{}
Another thing I've volunteered my time to is the OpenIndiana project, a list of
things I did include:
\par


\begin{itemize}
	\item{Recommended the switch from \href{https://www.atlassian.com/software/confluence}{Atlassian Confluence Wiki} to \href{http://www.mkdocs.org/}{MkDocs} to reduce project complexity.}
	\item {Helped to convert documentation from \href{https://www.atlassian.com/software/confluence}{Atlassian Confluence Wiki} to \href{http://www.mkdocs.org/}{MkDocs}.}
	\item {Contributed some of my own documentation from a past project.}
	\item {Helped setup and test \href{https://travis-ci.org/}{Travis CI}, a continuous integration service.}
\end{itemize}

\subsection{Photos for Culinary}
\paragraph{}
Another notable thing I've done is take photos for the cookbook that the DCMO
BOCES culinary class was making.
\par

\section{Dedication and Commitment}
\paragraph{}
One of the ways I have demonstrated my dedication is through the years of
passionate volunteering I have done at CyberTech.
\par
